Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-12 paper.tex
Updates from Overleaf

A simple example is the case of XA, illustrated in Figure~\ref{fig:pango-simple-origin-graph}A.
This shows a subgraph of the long ARG, in which paths have been traced above all
Nextclade-identified XA samples to the closest other sample strains in our dataset.
Dotted lines show where this subgraph links to other nodes within the ARG, and above
recombination nodes only
ancestral nodes are shown (i.e. cousins of the recombinant parents are omitted).
It is clear from the subgraph that all the XA samples trace to a single originating
recombination node (plotted in black), with a breakpoint position around 22227bp.

@@

Figure~\ref{fig:pango-simple-origin-graph}B shows a case of another
Pango lineage, XAG, whose Nextclade-designated samples also trace to a
single originating recombination. This is a more intricate example, as the same origin
is also shared with all samples designated XAA, and some, but not all, of the
samples identified as XAB, XQ, and XU by Nextclade. Note, however, that if the GISAID
designations are used, many of the samples marked here as XAB are reclassified
as BA.2, and XAG becomes fully monophyletic (supplementary figure
\ref{fig:pango_XAG_gisaid_graph}, which also gives identifying labels to the
sample nodes, convertable to EPI\_ISL identifiers using
Supplementary table XXX )

>>>>

A simple example is the case of XA, illustrated in Figure~\ref{fig:pango-simple-origin-graph}A.
This shows a subgraph of the long ARG, in which paths have been traced from all
Nextclade-identified XA samples to the closest other sample strains in our dataset.
Dotted lines show where this subgraph links to other nodes within the ARG, and above
recombination nodes only ancestral nodes are shown (i.e. we do not descent to include
cousins of recombinant parents).
It is clear from the subgraph that all the XA samples trace to a single originating
recombination node (plotted in black), with a breakpoint position around 22227bp.

@@

A more complex single-origin case is Figure~\ref{fig:pango-simple-origin-graph}B shows a case of another
Pango lineage, XAG, whose Nextclade-designated samples also trace to a
single originating recombination. This is a more intricate example, as the same origin
is also shared with all samples designated XAA, and some, but not all, of the
samples identified as XAB, XQ, and XU by Nextclade. Note, however, that if the GISAID
designations are used, many of the samples marked here as XAB are reclassified
as BA.2, and XAG becomes fully monophyletic (supplementary figure
\ref{fig:pango_XAG_gisaid_graph}, which also gives identifying labels to the
sample nodes, convertable to EPI\_ISL identifiers using
Supplementary table XXX )
